
%------------------------
% Resume Template - Revised for Internship (Data/Quant)
% Candidate: Chaoan Li
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{1pt}
\input{glyphtounicode}

\setlength{\footskip}{4.35004pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1}{: #2 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------
% START DOCUMENT
\begin{document}

% Header
\begin{center}
  {\Huge \scshape Chaoan Li} \\ \vspace{1pt}
  Ph.D. Student in Data Science, Texas A\&M University \\ \vspace{1pt}
  \small \faPhone\ 979-326-7515 \ \ \href{mailto:chaoan@tamu.edu}{\faEnvelope\ \underline{chaoan@tamu.edu}} \\
  \href{https://github.com/ChaoanLi}{\faGithub\ github.com/ChaoanLi} \quad 
  \href{https://chaoanli.github.io}{\faGlobe\ chaoanli.github.io}
  \vspace{-4pt}
\end{center}

% Objective
\section*{Objective}
Seeking a Summer 2026 internship in Data Science or Quantitative Research where I can apply my strong mathematical background, research skills, and proficiency in Python/R for solving real-world data problems.

% Education
\section*{Education}
\resumeSubHeadingListStart
\resumeSubheading{Texas A\&M University}{College Station, TX}{Ph.D. Student - Data Science}{Aug. 2024 -- Present}
\resumeSubheading{Beijing Normal University}{Beijing, China}{M.S. - Pure Mathematics; GPA: 3.5/4}{Sep. 2021 -- Jul. 2024}
\resumeSubheading{Univ. of Science and Technology Beijing}{Beijing, China}{B.S. - Mathematics and Applied Mathematics; GPA: 3.94/4}{Sep. 2017 -- Jul. 2021}
\resumeSubheading{Univ. of Science and Technology Beijing}{Beijing, China}{Second Major - Financial Engineering; GPA: 3.89/4}{Sep. 2018 -- Jul. 2021}
\resumeSubHeadingListEnd

% Publications
\section*{Publications}
\begin{itemize}
  \item C. Li, X. Yan and D. Yang, \textit{Anisotropic ball Campanato-type function spaces and their applications}, Anal. Math. Phys. 13 (2023), Paper No. 50, 71 pp.
  \item C. Li, X. Yan and D. Yang, \textit{Fourier transform of anisotropic Hardy spaces and applications to Hardy--Littlewood inequalities}, Acta Math. Appl. Sin. Engl. Ser (2024), \href{https://doi.org/10.1007/s10255-024-1124-5}{doi:10.1007/s10255-024-1124-5}.
\end{itemize}

% Projects
\section*{Projects}
\resumeSubHeadingListStart

\resumeSubheading{Local-Validation: Model-free Validation Tool}{Python, Simulation, Visualization}{\href{https://github.com/ChaoanLi/local-validation}{github.com/ChaoanLi/local-validation}}{2024}
\resumeItemListStart
\resumeItem{Purpose}{Developed a flexible validation tool for statistical functionals using kernel ridge regression.}
\resumeItem{Contribution}{Designed simulation pipelines to evaluate estimation accuracy under various sampling designs.}
\resumeItem{Application}{Useful for validating model performance in situations where standard assumptions may not hold.}
\resumeItem{Tech Stack}{Python, numpy, scipy, matplotlib.}
\resumeItemListEnd

\resumeSubheading{E-value Inference Toolbox}{R, Statistical Inference, Package Development}{\href{https://github.com/ChaoanLi/E-value}{github.com/ChaoanLi/E-value}}{2024}
\resumeItemListStart
\resumeItem{Purpose}{Implemented a general R framework for performing e-value based multiple hypothesis testing.}
\resumeItem{Contribution}{Designed functions for constructing e-processes, computing test statistics, and validating error control.}
\resumeItem{Tech Stack}{R, ggplot2, base plotting, custom S3 methods.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% Honors & Awards
\section*{Honors \& Awards}
\begin{itemize}
  \item 1st Prize Academic Scholarship, Beijing Normal University (2023)
  \item 2nd Prize of Mathematical Contest in Modeling, Beijing (2020)
  \item Outstanding Graduate, USTB (2021)
\end{itemize}

% Teaching
\section*{Teaching Experience}
\begin{itemize}
  \item Teaching Assistant, Functional Analysis – Led weekly discussions for 140+ undergraduates, Beijing Normal University (2022)
\end{itemize}

% Academic Engagement
\section*{Academic Engagements}
\begin{itemize}
  \item Participated in 2023 Beijing Harmonic Analysis conferences and assisted organizing sessions.
\end{itemize}

% Skills
\section*{Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Programming:} Python (NumPy, pandas, matplotlib, scikit-learn), R (ggplot2, dplyr), SQL, MATLAB, \LaTeX
  \item \textbf{Concepts:} Statistics, Machine Learning, Optimization, Time Series, Multiple Testing, E-values
  \item \textbf{Tools:} Git, VSCode, Jupyter Notebook, Overleaf
\end{itemize}

\end{document}
